Prefetching SPARQL query cacher

### 2016-05-18 dissertation/introdefhistory.tex
new section on objectivity

One such vision is the article by Berners-Lee, Hendler and Lassila in
Scientific American 2001\cite{berners2001semantic}, but it does not attempt such an
operational definition. Neither \cite{semwebroadmap} nor \cite{berners2000weaving} contains
such definitions. However, it is clear that an essential
characteristic of the Web, and by extension, the Semantic Web, is its
\emph{universality} and therefore, any actor should be as free as
possible to adapt it to their visions and needs, and so, a pursuit of
such a definition may not be desirable. Therefore, rather than
defining it, one should carefully declare one's visions.

@@

The following challenges several conventions of scientific
writing. Passive voice is generally overused in scientific writing,
sometimes because the author may think it emphasises the objectivity
of the investigation. In my opinion it rather attempts to hide the
fact that science is a human and social endeavour, and only by
acknowledging that fact, an investigator can properly account for
their own role. Double blind trials in medicine are an example of why
it is important to acknowledge the investigator's role. Moreover, the
use of ``we'', when it is clear that the work has been done by a
single investigator is inappropriate as it obscures
the role of the investigator.

As noted, the Semantic Web is a complex technical, social, economic
and cultural artefact. The objectivity of an investigator may be
challenged by a large intellectual investment in this artefact, the
more you want this artefact to succeed, the higher may your risk of
not being sufficiently objective be. I hereby declare that I have a
very large intellectual investment in the success of the Semantic Web,
and therefore this section is a reflection on my own role in the
development of this artefact. This serves to clarify \emph{my} vision
as well as aspects that may influence the objectivity of the
investigation.

>>>>

One such vision is the article by Berners-Lee, Hendler and Lassila in
Scientific American 2001\cite{berners2001semantic}, but it does not attempt such an
operational definition. Neither \cite{semwebroadmap} nor \cite{berners2000weaving} contains
such definitions. However, it is clear that an essential
characteristic of the Web, and by extension, the Semantic Web, is its
\emph{universality} and therefore, any actor should be as free as
possible to adapt it to their visions and needs. A pursuit of a
definition of the term ``Semantic Web'' would require a philosophical
treatment which would be beyond the scope of this thesis, and even
with that, may not be a fruitful exercise from a technical
perspective.

Therefore, rather than attempt a definition, understanding is rather
promoted by following the example of \cite{berners2001semantic} and
declare a vision.

\section{Objectivity of the study}

A vision has necessarily a strong personal element. This challenges
the ideals of objectivity in scientific investigations. A longer
discussion of the desirability and attainability of objectivity in
science is beyond the scope of this thesis, but objectivity can be
challenged from many different angles
\cite{sep-scientific-objectivity}.

The impact of the Web in particular and information technologies in
general, on society is great, and research projects are often funded
because of their relevance to society. With this perspective, this
research is hardly value-free. As individual researchers, we may
develop a strong relationship to the systems we create, as we have a
great intellectual investment in them. This may influence our ability
to reject a flawed hypothesis even if we should. Even though we note
in the discussion of the contributions in Section~\ref{sec:conphil}
the weaknesses of Thomas Kuhn's philosophy of science, his insistence
of understanding science as a social endeavour stands firm.

These challenges are inescapable, and therefore, it is important that
the researcher acknowledges such problems and explicitly details their
own personal motivations, visions and possible biases to let the
reader decide whether the researcher's subjective beliefs has
influenced the validity of their contribution.

I shall attempt to do so in the following, but also note that this
influences the writing style. There are several conventions of
scientific writing that stands in opposition to the goal of letting
the reader understand the possible influence of subjective
beliefs. The frequent use of passive voice is one such convention,
that in my opinion tries to hide subjectivity rather than alleviate
its harmful effects. If the methodology used in the investigation is
flawed, it should not be obscured by writing style, the methodology
will need to be enhanced. Double blind trials in medicine are an
example of why it is important to acknowledge the investigator's
role. That is not to say that the use of passive voice is always
inappropriate, when the role of the investigator cannot be
misunderstood, it can be used just like any other language construct.

Of less importance is the use of ``we'', when it is clear that the
work has been done by a single investigator. I hold as a general
principle that the role of the investigator should never be obscured,
and therefore, such use is inappropriate. The use of pronouns should
not differ substantially in scientific writing from other writing, and
I will use them accordingly. In particular, I will use ``we'' when
more than one person has been involved, or when the reader is included
(e.g. ``We note that...'').

@@

As noted in the previous section, objectivity may be challenged by a
researcher's intellectual investment in a certain field of study. I
admit that I have a very large intellectual investment in the success
of the Semantic Web. This section serves two purposes: It should give
the reader a good understanding of this intellectual investment, and
enable them to assess the impact of any subjective beliefs. Secondly,
it serves to clarify \emph{my} vision, which we noted in
Section~\ref{sec:nodef} is more important than to attempt a
definition. The vision strongly influences the motivation detailed in
Section~\ref{sec:motivation}.
